\section{Appendix}

\subsection{Cross-family robustness on FreshQA public runs}

\begin{table}[h]
\centering
\small
\input{../shared/generated/tab_freshqa_cross_family_official}
\caption{FreshQA cross-family robustness. The retrieval-dominant boundary survives the extension from the primary FLAN matrix to Qwen2.5-1.5B-Instruct and SmolLM2-360M-Instruct.}
\label{tab:appendix-public-cross-family}
\end{table}

The qualitative conclusion is unchanged across the four models. Retrieval remains perfect on both public slices. On the main slice, calibration helps relative to the full router, but \texttt{router\_no\_v\_future} remains much closer to retrieval. On the sequence slice, suppression of delayed utility is again safer than the full router, and calibration is inconsistent.

\subsection{Bundled controlled-update supplementary context}

\begin{table}[h]
\centering
\small
\input{../shared/generated/tab_freshness_bundled_official}
\caption{Appendix-only controlled-update diagnostic. This deterministic local benchmark is supplementary context rather than part of the external benchmark surface.}
\label{tab:appendix-freshness}
\end{table}

This appendix-only diagnostic is clearly separated from the external benchmark surface. In that deterministic stable-update setting, the full router reaches 0.867 quality versus 0.133 for retrieval-only, 0.600 for memory-only, and 0.800 for fast-adapt-only. The pattern is useful as supplementary context, but it does not override the FreshQA, MQuAKE, or UniEdit evidence.

\subsection{Evidence taxonomy and inspection guide}

The package separates four evidence surfaces explicitly:
\begin{itemize}[leftmargin=1.5em]
\item \textbf{Main evidence surface:} registry-listed official bundles under \texttt{artifacts/tmlr\_official/}, inspected through \texttt{manifest.json}, \texttt{aggregate\_table.md}, \texttt{run\_rows.jsonl}, \texttt{significance.json}, and \texttt{bootstrap.json}.
\item \textbf{Appendix-only supplementary diagnostic:} \texttt{artifacts/freshness\_v1/}.
\item \textbf{Manual audit:} \texttt{artifacts/tmlr\_official/freshqa\_leakage\_audit\_manual\_v1/}.
\item \textbf{Reliability notes:} \texttt{artifacts/tmlr\_official/mquake\_reliability\_note\_v1/} and \texttt{artifacts/tmlr\_official/uniedit\_reliability\_note\_v1/}.
\end{itemize}

All headline numbers in the paper are copied from frozen local bundle files only. The mapping from claims to exact source files is recorded in \texttt{paper/shared/claims\_to\_artifacts.md}, the official run registry is \texttt{paper\_run\_manifest\_index.json}, and dataset provenance is summarized in \texttt{DATASET\_MANIFEST.md}. A reader who wants to verify a claim can therefore follow a short path: registry entry, claims map, frozen bundle files, then dataset manifest.
