\section{MQuAKE: A Retrieval-Dominant Propagation Boundary}

MQuAKE asks a different question from FreshQA. The issue is not just whether an answer changed recently; it is whether an updated fact propagates correctly to direct edits, single-hop probes, and multi-hop consequences \citep{zhong2023mquake}. In our frozen official runs, this regime is also retrieval-dominant.

\begin{table}[h]
\centering
\small
\input{../shared/generated/tab_mquake_official}
\caption{Official MQuAKE results. Retrieval remains strongest on overall quality, direct edit success, and multi-hop consequences. Suppressing delayed utility improves on the full router but still does not overtake retrieval.}
\label{tab:mquake-main}
\end{table}

On both FLAN backbones, \texttt{always\_retrieve} reaches 0.551 overall quality. The full router reaches only 0.284 on FLAN-T5-Base and 0.276 on FLAN-T5-Small. The calibrated router is identical to the full router here, which means the public-answer calibration rule does not rescue the propagation regime. Suppressing delayed utility improves overall quality to 0.338 on FLAN-T5-Base and 0.319 on FLAN-T5-Small, but those gains still remain far below retrieval.

The benchmark-specific metrics make the boundary clearer. Retrieval reaches edit success 0.214, single-hop accuracy 1.000, and multi-hop accuracy 0.214 on both FLAN backbones. The full router lowers all three. The no-\(V_{\text{future}}\) ablation raises single-hop accuracy, but only by sacrificing direct edit success and especially multi-hop accuracy, which falls to 0.093 on FLAN-T5-Base and 0.031 on FLAN-T5-Small. Paired sign tests again show retrieval dominating with effectively zero \(p\)-values in both official FLAN bundles.

The main lesson is therefore negative but useful: delayed utility does not transfer safely from stable recurrence to propagation-heavy edits. Even removing delayed utility entirely is only a partial repair, because the strongest safe policy in this regime is still retrieval-dominant.
